### 2017-08-28 paper/incomeShocks-jde-r1.tex
Add table on whether prior behavior affects future shocks

% Reverse regressions - predictive or pseudo

\begin{table}[htbp]
\begin{center}
\begin{small}
\begin{threeparttable}
\caption{The Association between Prior Fertility and Contraceptive Use and Current Crop Loss}
\label{tab:reverse}
\begin{tabular}{@{} l D{.}{.}{2.6}  D{.}{.}{2.6} D{.}{.}{2.6} D{.}{.}{2.6} @{}}
\toprule
                                                       &\multicolumn{2}{c}{Crop loss - Dummy }& \multicolumn{2}{c}{} \\
                                                       &\multicolumn{2}{c}{200 TZS or above}       & \multicolumn{2}{c}{Log crop loss} \\ \midrule
                                                       & \multicolumn{4}{c}{Prior contraceptive use} \\
Used contraceptives prior survey                       &      -0.044         &      -0.034         &      -0.014         &      -0.013         \\
                                                       &     (0.049)         &     (0.054)         &     (0.012)         &     (0.012)         \\
Used contraceptives prior survey \X initial assets     &                     &      -0.001         &                     &      -0.000         \\
                                                       &                     &     (0.002)         &                     &     (0.000)         \\
\addlinespace 
                                                       & \multicolumn{4}{c}{Prior pregnancy} \\
Was pregnant prior survey                              &       0.017         &      -0.004         &       0.006         &       0.005         \\
                                                       &     (0.033)         &     (0.037)         &     (0.008)         &     (0.008)         \\
Pregnant prior survey \X initial assets                &                     &       0.003         &                     &       0.000         \\
                                                       &                     &     (0.002)         &                     &     (0.000)         \\
\addlinespace 
                                                       & \multicolumn{4}{c}{Prior birth} \\
Gave birth 7-14 months ago                             &      -0.034         &      -0.010         &      -0.002         &       0.003         \\
                                                       &     (0.029)         &     (0.031)         &     (0.007)         &     (0.008)         \\
Birth prior survey \X initial assets                   &                     &      -0.003\sym{**} &                     &      -0.001\sym{***}\\
                                                       &                     &     (0.001)         &                     &     (0.000)         \\
\addlinespace 
Wave dummies                                           &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        \\
Woman fixed effects                                    &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        \\
Observations                                           &    \mco{741}        &    \mco{741}        &    \mco{741}        &    \mco{741}        \\
Number of women                                        &    \mco{247}        &    \mco{247}        &    \mco{247}        &    \mco{247}        \\
\bottomrule
\end{tabular}
\begin{tablenotes} \footnotesize
\item \hspace*{-0.5em} \textbf{Note.}
Each panel a separate regression. 
Two left columns are linear probability models and two right columns 
are linear models.
Robust standard errors clustered at household level in parentheses; 
* significant at 10\%; ** significant at 5\%; *** significant at 1\%.
Crop loss is a dummy for a per capita crop loss of 200 TZS or above.
Assets are per capita and measured in 10,000 TZS.
Log crop loss is log per capita crop loss plus 1.
Log of assets are taken off assets per capita in TZS.
\end{tablenotes}
\end{threeparttable}
\end{small}
\end{center}
\end{table}

>>>>

% Reverse regressions - predictive or pseudo
\input{../tables/appendix_reverse.tex}
